---
title: "Griffin_Review Ambekar"
output:
  pdf_document: default
  html_document: default
---

###Brianna D. Griffin Review of Sushma Ambekar Assignment 

#General Comment: it would be nice if you use the ### symbols when writing comments as it makes it stand out on markdowns and easier to read in between your code

#File inspection looks nice, everything ran well 

#During the next section I kept getting and errors (though the code seems to have ran still) 
#your code line 167-172

```{r}
maize_melt <- melt(mac_filtered, id.vars =c("SNP_ID", "Chromosome", "Position"),variable.name = "corn",value.name = "base.composition")
```

# 'Warning message:attributes are not identical across measure variables; they will be dropped'

```{r}
teosinte_melt <- melt(tac_filtered, id.vars =c("SNP_ID", "Chromosome", "Position"),variable.name = "corn",value.name = "base.composition")
```

#'Warning message:attributes are not identical across measure variables; they will be dropped'

```{r}
ggplot(data=maize_melt) + geom_point(mapping=aes(x=Chromosome,y=Position), colour="red", alpha=0.01) + scale_x_discrete(limits=c(1:10)) + theme_classic()
```

#Warning message:Continuous limits supplied to discrete scale.Did you mean `limits = factor(...)` or `scale_*_continuous()`?'

```{r}
ggplot(data=teosinte_melt) + geom_point(mapping=aes(x=Chromosome,y=Position), colour="blue", alpha=0.01) + scale_x_discrete(limits=c(1:10)) + theme_classic()
```

#'Warning message:Continuous limits supplied to discrete scale.Did you mean `limits = factor(...)` or `scale_*_continuous()`? 

#I am not sure if these errors are important or not as it seems to have still ran without a problem, but maybe something worth looking into 

# 179 threw the same error (Cattributes are not identical across measre cariables)

#line 202 and 203 threw a different error 

```{r} 
ggplot(group_prop_melt,aes(x = Group, y= value, fill=variable)) + geom_bar(stat = "identity", position = "stack") + theme_classic() + theme(axis.text.x = element_text(angle = 90))
```

#Warning message:Removed 16 rows containing missing values (position_stack). 

```{r} 
ggplot(ID_prop_melt,aes(x = Sample_ID, y= value, fill=variable)) + geom_bar(stat = "identity", position = "stack") + theme_classic()
```

#Warning message:Removed 2782 rows containing missing values (position_stack). 

#again not sure if these are important as the code ran well and the graphs look awesome 

#Overall I had no issues and everything ran smoothly. I just wanted to bring the warning messages to your attention in case they didnt show up on your console.
#Nice job! 








